% Current Date and Time (UTC - YYYY-MM-DD HH:MM:SS formatted): 2025-07-14 16:22:02

\documentclass[a4paper,11pt]{article}

\usepackage[a4paper, top=0.2in, bottom=0.2in, left=0.2in, right=0.2in]{geometry}
\usepackage{url}
\usepackage{parskip}
\usepackage{color}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{adjustbox}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{enumitem}
\usepackage{supertabular}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}
\usepackage{tikz}
\usepackage{atbegshi}

\usepackage[colorlinks=true, linkcolor=black, urlcolor=black, citecolor=black, unicode=true, draft=false]{hyperref}

\begin{document}

\pagestyle{empty}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Johnathan Doe} \\[7.5pt]
\href{https://github.com/doe-engine}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \ \href{https://linkedin.com/in/johndoesandbox}{\raisebox{-0.05\height}\faLinkedin\ LinkedIn} \ $|$ \ \href{https://portgen-prototype.netlify.app/}{\raisebox{-0.05\height}\faGlobe \ Portfolio} \ $|$ \ \href{mailto:johndoe.dev@mailinator.com}{\raisebox{-0.05\height}\faEnvelope \ johndoe.dev@mailinator.com} \ $|$ \ \href{tel:+13125558821}{\raisebox{-0.05\height}\faMobile \ +13125558821} \\
\end{tabularx}



\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2019-2019 & MSc Artificial Intelligence from \textbf{University of Amsterdam} \hfill 85\% \\ 
2010-2014 & BFA Animation \& Interactive Media from \textbf{School of Visual Arts, NYC} \hfill 71\% \\
\end{tabularx}

\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
  \textbf{FreightTrack – Logistics Management Platform} \textbar \textit{Repository}~\href{https://github.com/doe-engine/freighttrack}{\raisebox{-0.1em}{\faGithub}} & &  \\
\end{tabularx}
\begin{tabularx}{\linewidth}{@{}X@{}}
  \begin{itemize}[leftmargin=*]
  \small
  \vspace{-0.8em} % <-- Between Project Title and Description
    \item FreightTrack is a scalable logistics and fleet tracking platform I built for international supply chains.
    \item It allows real-time route optimization using ML models, automates driver payroll tracking, and integrates with customs APIs.
    \item I implemented multilingual portals and client-specific admin dashboards.
  \end{itemize}
\end{tabularx}
\vspace{-0.6em} % Between Projects

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
  \textbf{MyVoice – Crowdsourced Policy Feedback Tool} \textbar \textit{Repository}~\href{https://github.com/doe-engine/myvoice}{\raisebox{-0.1em}{\faGithub}} & &  \\
\end{tabularx}
\begin{tabularx}{\linewidth}{@{}X@{}}
  \begin{itemize}[leftmargin=*]
  \small
  \vspace{-0.8em} % <-- Between Project Title and Description
    \item I developed this web app to promote civic participation by allowing citizens to give structured feedback on policies.
    \item It uses NLP for sentiment analysis and user clustering and integrates with government dashboards for real-time updates.
    \item I also built a custom visualization engine to show impact heatmaps and demographic trends.
  \end{itemize}
\end{tabularx}
\vspace{-0.6em} % Between Projects

\begin{tabularx}{\linewidth}{ @{}l X r@{} }
  \textbf{StackPilot – Cloud Cost Optimizer} \textbar \textit{Repository}~\href{https://github.com/doe-engine/stackpilot}{\raisebox{-0.1em}{\faGithub}} \textbar \textit{Deployment}~\href{https://github.com/doe-engine/stackpilot}{\faGlobe} & &  \\
\end{tabularx}
\begin{tabularx}{\linewidth}{@{}X@{}}
  \begin{itemize}[leftmargin=*]
  \small
  \vspace{-0.8em} % <-- Between Project Title and Description
    \item I  created StackPilot to help teams monitor and reduce cloud infrastructure costs.
    \item It includes anomaly detection, usage heatmaps, and policy enforcement.
    \item I also built Kubernetes plugins for auto-tagging and archiving idle resources.
  \end{itemize}
\end{tabularx}

\section{Experience}
\large{\textbf{Senior Full Stack Developer}} - \textit{Synapse Fintech} \hfill (\textit{March 2018 - December 2021}) \\\vspace{-1.5em}
\begin{itemize}[leftmargin=*, itemsep=-0.5em]
    \item I designed and developed cloud-native microservices for a secure wealth management platform.
    \item I built dynamic UIs using React and Vue while managing data pipelines with Node and Python.
    \item I introduced CI/CD pipelines that reduced deployment time by 70\%.
\end{itemize}\vspace{-0.3em}

\large{\textbf{Lead Game Systems Architect}} - \textit{MindMesh Studios} \hfill (\textit{January 2022 - Present}) \\\vspace{-1.5em}
\begin{itemize}[leftmargin=*, itemsep=-0.5em]
    \item I led the technical design and backend architecture of multiplayer game engines supporting real-time decision-making and procedural storytelling.
    \item I collaborated closely with narrative teams and AI specialists to create reactive environments that evolve with player input.
    \item I also oversaw code optimization for scalability across platforms.
\end{itemize}

\section{Technical Skills}
\begin{itemize}[leftmargin=*]
    \setlength\itemsep{-0.5em}
    \item \textbf{Design \& Creativity:} Adobe Premiere Pro, Figma, Canva, After Effects
    \item \textbf{Web Development:} JavaScript, TypeScript, HTML, CSS, Tailwind CSS
    \item \textbf{Programming Languages:} Python, Java, C++. C, C\#
    \item \textbf{Database \& ORM:} PostgreSQL, MySQL
    \item \textbf{Data Science \& ML:} Pandas, Numpy, Scikit-Learn, Tensorflow, Matplotlib
\end{itemize}

\section{Certifications \& Achievements}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*, align=left]
    \item Certified Data Engineer – Associate, Google Cloud 
    \hfill \textit{(March 2023)}

    \item Unity Certified Programmer 
    \hfill \textit{(September 2017)}

    \item Agile Software Development (Scrum Master) 
    \hfill \textit{(April 2025)}

    \item Certified Kubernetes Administrator (CKA) 
    \hfill \textit{(September 2018)}

    \item AWS Certified Machine Learning – Specialty 
    \hfill \textit{(July 2018)}

    \item Advanced Game AI Design 
    \hfill \textit{(March 2012)}
\end{itemize}

\AtBeginShipout{%
  \AtBeginShipoutUpperLeft{%
    \begin{tikzpicture}[remember picture, overlay]
      \node[anchor=south, yshift=5pt] at (current page.south) {\footnotesize Last updated: \today};
    \end{tikzpicture}%
  }%
}

\end{document}